---
title: "NEWS"
author: Erik.Leppo@tetratech.com and jon.harcum@tetratech.com
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```
baytrendsmap 0.0.3.9008
===========
Released - 2019-11-18

* Fix Up Is Good, Issue #5

    + Trend Map, change color only, not direction.

* ui.R

    + App title to use package version as defined in global.R.

baytrendsmap 0.0.3.9007
===========
Released - 2019-11-06

* Fixed Zoom code.  Issue #4.

* Added vignette for use with pkgdown website.

* DESCRIPTION

    + Add URL of pkgdown website.

baytrendsmap 0.0.3.9006
===========
Released - 2019-11-06

* Add custom breaks/classes for range map.  Issue #3.

* Add filtered data set for testing.

* Zoom code not working so commented out.  Issue #4

* Restructured NEWS.

baytrendsmap 0.0.3.9005
===========
Released - 2019-11-05

* Add a pkgdown website.

* Replace map zoom code with plotly.  Issue #4

baytrendsmap 0.0.3.9004
===========
Released - 2019-10-31

* Shiny, Maps

    + Add zoom feature, Issue #4
    
    + Fixed ratio of 1.3 (better sizing).
    
* Miscellaneous formatting.
    
baytrendsmap 0.0.3.9003
===========
Released - 2019-10-30

* Shiny

    + Map, Trend, Add point outlines, Issue #2.
    
* NEWS

    + Keep NEWS.md file rather than delete.
    
    
baytrendsmap 0.0.3.9002
===========
Released - 2019-10-30

* Shiny

    + Map, Range, Add point outlines, Issue #2.
    
    + Update Help text., Issue #1
    
baytrendsmap 0.0.3.9001
===========
Released - 2019-10-29

* Shiny

    + Update Help screen, Issue #1.

baytrendsmap 0.0.3
===========
Released - 2019-09-24

* Release stable version with updates.

baytrendsmap 0.0.2.9002
===========
Released - 2019-09-24

* Filter

    + Update "clearFilters" button.

baytrendsmap 0.0.2.9001
===========
Released - 2019-09-24

* global.R

    + Test map zoom in global.
    
    + Make Shiny load silently as well.
    
* Added 2nd test data file.

* tab_Data.R

    + Fix typo.
    
* Trend map

    + NS points
    
        - Change "gray" to "dark gray".
        
    + Modified (removed debug mode):
    
        - UpisGood
        
        - p value significant threshold
        
        - p value possible threshold
        
    + Proper map is created for title and river names.
    
* Range map

    + "Pretty" option ignores number of breaks.
    
        - Added error trapping to use number of breaks output from pretty option.
        
* Filters

    + Add "ClearFilters" button.
    
        - Inactive at this point.

baytrendsmap 0.0.2
===========
Released - 2019-09-19

* Interim release.

baytrendsmap 0.0.1.9013
===========
Released - 2019-09-19

* Trends map

    + Edits to global test.
    
    + Create Trends tab; similar to Range tab.
    
    + Create map. 
    
* Remove dynamic version number from title.

    + Causes Shiny.io to fail.
    
* global

    + Base map declare fill color so don't use scale_fill_manual.
    
* tab_Filter

    + Reorder tabs with filter summary before data.
    
    + Rename data tabs.
    
baytrendsmap 0.0.1.9012
===========
Released - 2019-09-18

* Trends map, legend to include range of values.

* DESCRIPTION; add packages

    + Add grid, lubridate, and sp
    
* global.R

    + Suppress messages
    
        - library
        
        - readOGR
        
        - fortify
        
* range map

    + Add button to auto-generate map title based on filtered selections.
    
    + Make auto-title wrap lines.
    
    + Add cut (break) numbers to legend.

baytrendsmap 0.0.1.9011
===========
Released - 2019-09-18

* Add number of non-"one" entries on "Data Filter Summary" tab.

* Modifty title to include dynamic package version number.

baytrendsmap 0.0.1.9010
===========
Released - 2019-09-05

* DESCRIPTION

    + Reduced required R version from 3.6.0 to 3.2.0.
    
    + Matches baytrends package.

baytrendsmap 0.0.1.9009
===========
Released - 2019-09-04

* Returned to use of shp file.

baytrendsmap 0.0.1.9008
===========
Released - 2019-09-04

* GIS shapefile (cbpseg) to RDA.

    + Speed and file size improvement.

baytrendsmap 0.0.1.9007
===========
Released - 2019-09-03

* Range map working.

baytrendsmap 0.0.1.9006
===========
Released - 2019-08-30

* Range map selection buttons (not finished).

baytrendsmap 0.0.1.9005
===========
Released - 2019-08-29

* Range map options.

* Default Range map.


baytrendsmap 0.0.1.9004
===========
Released - 2019-08-29

* Add dplyr package to global and DESCRIPTION.

    + Need for filter summary table.

baytrendsmap 0.0.1.9003
===========
Released - 2019-08-29

* Filters working.

* Structure for maps.

* Filter summary so can find non-uniques and re-apply filters.

* Packages to global.R.

* Package updates to DESCRIPTION.

baytrendsmap 0.0.1.9002
===========
Released - 2019-08-28

* Filters and other additions.

baytrendsmap 0.0.1.9001
===========
Released - 2019-08-26

* Redesign interface.

baytrendsmap 0.0.0.9005
===========
Released - 2019-08-23

* Add test data to create new map.

* Modify Shiny app to use imported data file.

baytrendsmap 0.0.0.9004
===========
Released - 2019-08-21

* Update Readme with usage directions.

baytrendsmap 0.0.0.9003
===========
Released - 2019-08-21

* Update Readme with installation directions.

baytrendsmap 0.0.0.9002
===========
Released - 2019-08-21

* Updated repository with working files.

* Rename without underscore to baytrendsmap.

baytrendsmap 0.0.0.9001
===========
Released - 2019-08-21

* Initial commit to GitHub
