---
title: "NEWS"
author: Erik.Leppo@tetratech.com and jon.harcum@tetratech.com
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```
baytrendsmap 0.0.1.9003
===========
* Released - 2019-08-29
* Filters working.
* Structure for maps.
* Filter summary so can find non-uniques and re-apply filters.
* Packages to global.R.
* Package updates to DESCRIPTION.

baytrendsmap 0.0.1.9002
===========
* Released - 2019-08-28
* Filters and other additions.

baytrendsmap 0.0.1.9001
===========
* Released - 2019-08-26
* Redesign interface.

baytrendsmap 0.0.0.9005
===========
* Released - 2019-08-23
* Add test data to create new map.
* Modify Shiny app to use imported data file.

baytrendsmap 0.0.0.9004
===========
* Released - 2019-08-21
* Update Readme with usage directions.

baytrendsmap 0.0.0.9003
===========
* Released - 2019-08-21
* Update Readme with installation directions.

baytrendsmap 0.0.0.9002
===========
* Released - 2019-08-21
* Updated repository with working files.
* Rename without underscore to baytrendsmap.

baytrendsmap 0.0.0.9001
===========
* Released - 2019-08-21
* Initial commit to GitHub
