---
title: "Navigating the baytrendsmap Shiny App"
#subtitle: "help"
#author: "`r Sys.getenv('USERNAME')`"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output:
  html_document:
    toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(results='asis', echo=FALSE, warning=FALSE)
```

1. In R studio (or base R), run these 2 lines to open up the shiny app:

```{r runShiny, eval=FALSE, echo=TRUE}
library(baytrendsmap)
runShiny()
```

2. Once open, in tab "1. Import Data" use the "Browse" button to select your desired `baytrends` package output.

3. Before continuing be sure the data file loaded into the app.  That is, wait for the blue progress bar to read "Upload complete".  When the upload is complete a data table will appear in the main window to the right.

4. Click on "2. Filter Data", and notice that it says "308 = Number of entries with more than 1 record". It is necessary to filter this data set down until the message here tells you "0" entries have more than 1 record. Our csv files have results for different periods, seasons, models and depths for each station. To make the app work, you need to filter it down to 1 record per station. This may be a little tough if you aren’t familiar with the files because they don’t all contain the same choices.

a) If the imported data are not in the proper format then "red" error messages will appear in the main window on the right instead of a data table.

5. Make the following selections in the blue buttons on the left in order to filter down this specific file that I’ve attached.
a) Filter by 'Gam Formula Name': Click Deselect All, then use the drop down to pick just one of these, e.g., "2- Non-linear".
b) Filter by 'sample Layer': same thing, deselect, then select one, e.g., "B".
c) Filter by 'Period Name': Select just one of these, e.g., "Full Record".
d) Filter by 'Season Name': Select just one, e.g., "Summer1".

6. Don’t click the bottom button, but scroll back to the top and click “Apply Filters”. Now you should see the text say 0=Number of entries with more than 1 record.

7. Click on the 2nd blue tab called “Filter Data”. This is now the table of data that will be mapped.

8. Click on “Range Map”. You have to make a selection in each of the blue boxes under 3.a. Range Map Options. An error can occur if one is skipped. Make a selection for each, they should all work as they are subsets from the current data file. Then click “Update Range Map” at the top.

9. Click on the “Trend Map” tab. Pick something in each of the filter otherwise an error occurs.  Click “update trend map”.